\section{Beyond the superficial}
Machine learning is a technology that is here to stay, as software engineers, it is important to understand the social impacts of the technology we develop. Given the world is now more interconnected as well as polarized, there is a high importance in the way that technology affects all possible types of customers. In the case of DigiPen students, there are a lot of game developers that work with peripherals that might be using machine learning, understanding how the technology affects your players is important to ensure that they can have a good time and the art being made is not solely for a privileged majority.

On the case of other DigiPen students, there are some that go into embedded/imaging systems. Given the growth of this technology towards self-driving vehicles and robotics, it is very important as an engineer to try and acknowledge the ways in which your algorithms weigh different individuals involved. Be it from a medical device's ability to properly find patterns across a wide range of patients to a robotic arm at a factory being able to properly identify the other workers to ensure safety.

At a personal level, the greatest take away is that technology moves really fast compared to all the available support systems. This is scary but the fear is not for silence, it's more of an encouragement for me to make the world a better place through my work while being conscious of what I bring to the table. As discussed in the first paper for this class, I believe that reliable software is a requirement for software to bring value to society. This belief extends to this, for a system to be reliable it must provide answers at a deterministic level or substantially so. The usage of machine learning is not deterministic but also provides several benefits to society but a reliable system knows exactly what issues it has and how it can be overcome either through itself or other external systems.
