\section{Ethical Analysis}
With the context required, it is now possible to evaluate the salient issues presented by the documentary. While all questions will be evaluates using workable ethical frameworks, they will be different due to the compatibility between the question and the framework's ability to judge it without devolving to relativism.

\subsection{Responsibilities of ML companies}
When an ML company decides to produce a model, what are the responsiblities do they have towards all the involved stake-holders? The lack of governance over ML implementations has brought up the need to discuss what are the expectations towards a company's model.

\subsubsection{Kantianism}
Under Kantianism, companies are presented with the following formulations when it comes to a model's bias:

\begin{enumerate}
	\item{If a user damages someone with my product, it was a user's error}
	\item{Lying to others is ethically sound if I don't know better}
	\item{Making money off models that misrepresent people is ethical}
\end{enumerate}

For these formulations it can be seen that there are major contradictions. If everyone could blame their clients for the mistakes that their products make there would be no trust in any industry and therefore no development. For the second formulation runs into a contradiction, where if everyone were allow to spread misinformation, there would be no source of truth for humanity. Lastly, the 3rd formulation is removing humanity out of the minorities in the situation by neglecting the pain that the misrepresentation can cause. Evidence of this pain can be seen in the documentary as people of color are persecuted unfairly which causes them great distress and removes their agency when being judged. (CITE SOURCES HERE)

\subsubsection{Social Contract Theory}
Under social contract theory, instead of evaluating imperatives, there are implicit expectations that we as a society agree upon when integrating a system where machine learning is used:

\begin{enumerate}
	\item{The algorithm will measure biases impartially as it has no previous lived experiences}
	\item{The companies are developing the product with the goal of betterment of society with financial gain as compensation (as is the case with most development under capitalism)}
\end{enumerate}

As seen in the technical section, ML models do not poses the ability to be impartial as they reflect the biases of the sources without major human intervention which does not reflect the current usage of the tool. (ADD SOURCES HERE)

\subsubsection{Act Utilitarianism}
Compared to the other frameworks, the answer to our question can be evaluated via the maximization of the collective joy of people. Under this, it is hard to account for all possible factors but there is a majority which would benefit from the reduced cost of the models. However, discrimination brings issues to a population at large regardless of their level of privilege (SOURCE HERE). This helps reframe the possible measurements of joy from members of the majority to members of the minority to a measurement of how much the joy of an entire population weighs against those benefiting from the harm being caused by implementing models without strict regulation and cost. (ADD SOURCE HERE)

In 2025, it was reported that Immigration Customs Enforcement (ICE) in the USA has been utilizing a mobile app for identifying undocumented immigrants. That same year there had been several cases where citizens and documented immigrants were being unlawfully deported. On the other hand, using machine learning for law enforcement can greatly enhance safety when used correctly such as processing body camera footage from cops, predict threats via behavioral patterns and provide support to those who need it. Therefore, this makes the value society can get from it heavily vary in the fairness of the models used making it unethical with the current state of the technology. (ADD SOURCES HERE)

\subsection{Stakeholders responsible for damage}
When approaching the issue of creating legislation for ML models, there is a need to focus on the damages and how ethical frameworks can represent the damage being done:

\subsubsection{Social Contract Theory}
Under social contract theory, there is the ideal of assigning conditions before getting a role but in practice it functions the opposite. This causes an issue to arise when dealing with the responsibilities as a veil of ignorance can't really be kept as the models are already owned and managed by a select few. Because of this, it is important to focus on the pre-existing contracts established by society such as discrimination being harmful and harm being bad.

In this case, the main difference from an individual discriminating another is the discrimination is a sequence of processes. First, the data is collected from sources that carry bias, then the models are trained on this biased data and sometimes iterated upon to reduce bias. From there the ML company sells the model to a client without clearly labelling the bias in the model then a client proceeds to use it. As there are 2 beneficiaries of this technology, in social contract theory it is part of the contract that lying to clients is unethical, both from the ML company and the client company cases. From this, it is possible to determine that the ML company is complicit in the damage caused by the client's usage as they may not provide transparency in the model's bias. On the other hand, the client company is responsible for the damage they caused for not verifying their products would not harm their customers. This is because under social contract, people agree that lying and hurting your customer base is unethical.

\subsubsection{Virtue Ethics}
In virtue ethics, the assessment of who is responsible can be seen through the virtues of honesty and fairness. With this said, it can be seen that if machine learning algorithms discriminate in the hiring process, it is doing an unfair judgement, the person responsible for that judgement would be the person who decided to use the machine's verdict to determine such a thing. This shows that they were not practicing the virtues of fairness as they trusted a weighted model. In the case the model was not labelled as biased the party to blame is the development team for their lack of honesty in their sale of a model.

\subsection{Ethical feasibility of enforcing regulations}
As discussed in the previous sections, there are several issues that arise with the usage of machine learning to judge individuals, however, it is important to evaluate whether these processes can be purified to be ethical. This is a major issue as providing a product free of bias would mean it needs a lot of data refinement without guarantee that it will be rid of biases.

\subsubsection{Kantianism}
Kantianism is based on principles of universality, this means that if a formulation can be applied universally without contradiction, it is ethical. Therefore, the formulation "a machine is allowed to judge an individual unfairly" would devolve into the issue where machines could be used for increasingly more harmful things such as judging whether someone lives or not by having access to a job, healthcare or criminal punishment. If this were the case it would create a situation where machines are used to disregard other individual's humanity. Therefore making it unethical under Kantianism unless the model is proved to be fair, which is impossible with the current technologies.

\subsubsection{Act Utilitarianism}
Unlike the previous framework, the usage of a model can be ethical if the benefits outweigh the negatives. As discussed in the responsibilities of stakeholders, there is a very big emphasis on whether the model can produce numerical gains. This provides a stronger argument for using models in surveillance as they will keep the majority safe while the people who get affected are not as accounted for. The bigger issue is that just like mentioned in the previous categories, discrimination hurts the group in the long term as intra-group conflict causes more damage in terms of happiness and sustainability. Therefore, the ethical aspect of these models provides a larger loss in the case that it discriminates to a substantial extent. On the other hand, if these systems work a reasonable amount, it could be considered ethically sound.

\section{Conclusion}
To conclude, machine learning models pose several benefits in terms of technology and the ability to make infinitely adaptable algorithms. Just like any powerful tool, it must be managed for good, if the goals of machine learning companies is simply to make money, this is not guaranteed to bring betterment to society. Therefore, it is important to ensure there is regulation and incentive for machine learning developers, researchers and clients to seek to improve their practices. By looking at the ethical frameworks it was possible to derive that there isn't a single stakeholder to blame but it is more of a collective effort between the general public, the government and the companies that use/sell machine learning systems. In the documentary, there is a scene where they mention that this is a continuous effort and that regulation is not a one and done, which is reflected by the last question asked by this paper, these models reflect the bias in society therefore to use them more ethically the bias must be either acknowledged or the models must remain unused at all. On the more optimistic side, there is a lot of research into optimizing the fairness of models as removing bias has a lot of incentives beyond removing the biases towards people. The commercial incentive might drive the technology to develop to the point models meet the ethical requirements for a better world.
